---
title: "Workout 3"
author: "Amy Jian"
date: "5/3/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Overview
'binomial' is a package that implements functionsfor calculating probabilities of a binomial random variable and other related caculations such as the probability distribution and expected value.

* 'bin_choose( )' computes number of combinations of k successes in n trials
* 'bin_probability( )' computes 
* 'bin_distribution( )' creates a 'bindis' object, a data frame of the probability distribution
* 'bin_cumulative( )' creates 'bincum' object, a data frame of the cumulative probability distribution
* 'plot( ) method for 'bindis' and 'bincum' objects to plot probabilities of successes
* 'bin_var' creates a 'binvar' object
* 'summary( )' method for 'binvar' object
* individual summary measures:
    * 'bin_mean( )'
    * 'bin_variance( )'
    * 'bin_mode( )'
    * 'bin_skewness( )'
    * 'bin_kurtosis( )'

##Usage
```{r}
library(binomial)
```
```{r}
#number of combinations of 3 successes in 5 trials
bin_choose(n = 5, k = 3)
```
```{r}
#probability of 3 successes in 5 trials with success probability 0.7
bin_probability(success = 3, trials = 5, prob = 0.7)
```
```{r}
#binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.7)
dis1
```
```{r}
#plot probability distribution
plot(dis1)
```
```{r}
#binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.7)
dis2
```
```{r}
#plot cumulative distribution
plot(dis2)
```
```{r}
#binomial random variable
bin <- bin_variable(trials = 5, prob = 0.7)
bin
```
```{r}
#summary of a binomial random variable
summary(bin)
```
```{r}
#indiviudal summary measures
bin_mean(trials = 5, prob = 0.7)
bin_variance(trials = 5, prob = 0.7)
bin_mode(trials = 5, prob = 0.7)
bin_skewness(trials = 5, prob = 0.7)
bin_kurtosis(trials = 5, prob = 0.7)
```

